FitBit Analysis

### 2022-11-21 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
präsentation fitbit timeline + plot

@@

>>>>

# Überblick Datenerhebung

```{r timeline, fig.align = "center", echo = FALSE}

knitr::include_graphics("./images/timeline_fitbit.png", dpi = 130)

@@

# Plot für einzelne Phasen

```{r, fig.height = 8, fig.width = 15}

main %>% 
  filter(time_span != "overall") %>% 
  select("ID","time_span", "time","heart_rate") %>% 
  mutate(status = case_when(ID < 200 ~ "Unerfahren",
                            ID > 200 ~ "Erfahren"),
         time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Intviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Intviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
ggplot(mapping = aes(x = time,
                     y = heart_rate
                     )
       ) +
  stat_smooth(geom = "line",
              mapping = aes(color = status),
              method = "loess",
              se = FALSE) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  theme_apa() +
  facet_grid(cols = vars(time_span),
             scales = "free_x",
             )
